```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

data <- sc_questions %>%
  filter(`Service ID` == id)

# Encoding(data$`Mayor's  Action Plan`) <- "UTF-8"
# Encoding(data$Resiliency) <- "UTF-8"
# Encoding(data$Equity) <- "UTF-8"

budget <- summary %>%
  filter(`Service ID` == id) %>%
  ungroup() %>%
  select(-`Agency Name`, -`Agency Name - Cleaned`, -`Service ID`, -`Service Name`, -`FY24 Dollars - PROP`, -`FY24 Positions - PROP`)

colnames(budget) <- c("Fund", "Actual $", "Actual Pos", "Adopted $", "Adopted Pos", "CLS $", "CLS Pos")

```
*The Bureau of the Budget and Management Research Budget Proposals*

## Service: `r service`

**Agency Name**: `r agency`

**Pillar**: `r pillar`

**Service Description**: `r description`

### Budget Information

*Budget data is from BPFS as of December 28, 2022. This data may differ from what was entered into Scorecard's Fiscal 2024 Proposed Budget.*

```{r budget_summary, echo = FALSE, results = 'asis', warning=FALSE, out.width="100%"}
##replace budget data source

budget %>% 
  adorn_totals(fill = 0) %>%
  format_table_numbers() %>%
  knitr::kable(format = "latex", escape = TRUE, booktabs = TRUE, align = c("l", rep("r", 6))) %>%
  kable_styling(latex_options = c("striped","HOLD_position")) %>%
  add_header_above(c("Funds" = 1, "FY22" = 2, "FY23" = 2, "FY24" = 2), bold = TRUE) %>%
  row_spec(dim(budget)[1]+1, bold = TRUE) %>%
  row_spec(0, bold = TRUE)

```

### Budget Proposal

**FY24 Proposed Budget**: `r scales::dollar(fy24_dollars)`

**FY24 Proposed Positions**: `r fy24_positions `


```{r budget_proposal, echo = FALSE, results = 'asis', warning=FALSE, out.width="100%"}

df <- data %>%
  select(`Budget Proposal`) %>%
  # separate(`Budget Proposal`, into = c("Budget", "Question 1", "Question 2", "Question 3"), sep = "\\s+[1-3].\\s") %>%
  separate(`Budget Proposal`, into = c("Budget", "Question 1"), sep = "(1[.]\\s)") %>%
  separate(`Question 1`, into = c("Question 1", "Question 2"), sep = "(2[.]\\s)") %>%
  separate(`Question 2`, into = c("Question 2", "Question 3"), sep = "(3[.]\\s)") %>%
  mutate(`Question 1` = str_replace(`Question 1`, "Explain any budget changes between the Fiscal 2024 CLS Budget and Fiscal 2024 Proposed Budget.",""),
         `Question 2` = str_replace(`Question 2`, "Explain any staffing changes between the Fiscal 2024 CLS Budget and Fiscal 2024 Proposed Budget.",""),
         `Question 3` = str_replace(`Question 3`, "Describe how these changes impact service delivery.",""))

# cat(paste(df$`Question 1`, "\n\n"))
# 
# cat(paste(df$`Question 2`, "\n\n"))
# 
# cat(paste(df$`Question 3`, "\n\n"))

# cat(ifelse(nchar(df$`Question 1`) <= 94, paste(df$`Question 1`, "\n\n", "No answer provided", "\n\n"), paste(df$`Question 1`, "\n\n")))
# 
# cat(ifelse(nchar(df$`Question 2`) <= 96, paste(df$`Question 2`, "\n\n", "No answer provided", "\n\n"), paste(df$`Question 2`, "\n\n")))
# 
# cat(ifelse(nchar(df$`Question 3`) <= 51, paste(df$`Question 2`, "\n\n", "No answer provided", "\n\n"), paste(df$`Question 3`, "\n\n")))

```

1. Explain any budget changes between the Fiscal 2024 CLS Budget and Fiscal 2024 Proposed Budget.

```{r Q1, echo = FALSE, results = 'asis', warning=FALSE}

cat(df$`Question 1`)

```

2. Explain any staffing changes between the Fiscal 2024 CLS Budget and Fiscal 2024 Proposed Budget.

```{r Q2, echo = FALSE, results = 'asis', warning=FALSE}

cat(df$`Question 2`)

```

3. Describe how these changes impact service delivery.

```{r Q3, echo = FALSE, results = 'asis', warning=FALSE}

cat(df$`Question 3`)

```

### Service Questions and Responses

#### Mayor's Action Plan
```{r MAP, echo = FALSE, results='asis', warning = FALSE}

df <- data %>%
  select(`Mayor's  Action Plan`) %>%
  separate(`Mayor's  Action Plan`, into = c("Question 4", "Question 5", "Question 6"), sep = "\\s+[4-6].\\s") %>%
  mutate(`Question 4` = str_replace(`Question 4`, "4. ", ""),
         `Question 4` = str_replace(`Question 4`, "What.+\\?\\s+",
                             ""),
          `Question 5` = str_replace(`Question 5`, "What.+\\?\\s+",
                              ""),
          `Question 6` = str_replace(`Question 6`, "Describe.+goals and actions.\\s+",
                              ""))

# cat(paste(df$`Question 4`, "\n\n"))
# 
# cat(paste(df$`Question 5`, "\n\n"))

# cat(df$`Question 6`)

```

4. What goal(s) from the Mayor's Action Plan does this service connect to? The Goal identified should be from the Pillar this service is tied to.

```{r Q4, echo = FALSE, results = 'asis', warning=FALSE}

cat(df$`Question 4`)

```

5. What action(s) from the Mayor's Action Plan does this service connect to? The Action identified should be from the Goal identified above.

```{r Q5, echo = FALSE, results = 'asis', warning=FALSE}

cat(df$`Question 5`)

```

6. Describe how this service's activities help achieve the goal(s) and action(s) identified. List specific actions planned for FY2024 that are tied to these goals and actions.

```{r Q6, echo = FALSE, results = 'asis', warning=FALSE}

cat(df$`Question 6`)

```

#### Equity
```{r equity, echo = FALSE, results = 'asis', warning = FALSE}

df <- data %>%
  select(Equity) %>%
    separate(Equity, into = c("Equity Description", "Question 7", "Question 8"), sep = "\\s+[7-8].\\s") %>%
  mutate(`Question 7` = str_replace(`Question 7`, "7. ", ""),
         `Question 8` = str_replace(`Question 8`, "8. ", ""),
         `Equity Description` = str_replace(`Equity Description`, "Service Delivery & Equity", ""),
         `Question 7` = str_replace(`Question 7`, "What.+\\?\\s+", ""),
        `Question 8` = str_replace(`Question 8`, "What.+\\?\\s+", ""))

cat(paste0("*", df$`Equity Description`, "*", " \n\n"))

# cat(paste(df$`Question 7`, "\n\n"))
# 
# cat(df$`Question 8`)

```

7. What specific disparities does this service seek to address? How does this service address these disparities?

```{r Q7, echo = FALSE, results = 'asis', warning=FALSE}

cat(df$`Question 7`)

```

8. What data is used to assess the service's impact on reducing these disparities?

```{r Q8, echo = FALSE, results = 'asis', warning=FALSE}

cat(df$`Question 8`)

```

#### Resiliency
```{r resiliency, echo = FALSE, results = 'asis', warning = FALSE}

df <- data %>%
  select(`Resiliency`) %>%
  separate(Resiliency, into = c("Resiliency Description", "Question 9"), sep = "               ") %>%
  mutate(`Question 9` = str_replace(`Question 9`, "9. ", ""),
         `Resiliency Description` = str_replace(`Resiliency Description`, "Service Delivery & Resiliency", ""),
         `Question 9` = str_replace(`Question 9`, "Explain.+past.\\s", ""))

cat(paste0("*", df$`Resiliency Description`, "*", " \n\n"))
# 
# cat(df$`Question 9`)

```

9. Explain how this service adapts and adjusts in response to the changing needs of your end users. If possible, provide examples of how this service is doing this currently or has done this in the past.

```{r Q9, echo = FALSE, results = 'asis', warning=FALSE}

cat(df$`Question 9`)

```


### Performance Data
```{r pm_table, echo = FALSE, warning = FALSE, out.width = "100%"}
  
output <- sc_pms %>% filter(`Service ID` == id) %>%
  select(Measure:`Target 2024`)

colnames(output) <- c("Measure", "Actual", "Target", "Actual", "Target", "Actual", "Target", "Target")

output %>%
  knitr::kable(format = "latex", escape = TRUE, booktabs = TRUE, align = c("l", rep("r", 7))) %>%
  kable_styling(latex_options = c("striped","HOLD_position")) %>%
  add_header_above(c("Measure" = 1, "2021" = 2, "2022" = 2, "2023" = 2, "2024" = 1), bold = TRUE) %>%
  column_spec(1, width = "2in") %>%
  row_spec(0, bold = TRUE)

```



```{r curve, echo = FALSE, warning = FALSE, results='asis'}

df <- sc_story %>%
  filter(id == `Service ID` & !grepl("MOSS|Copy", `Measure`)) %>%
  select(Measure, `Note Text`, `Modify Date`) %>%
  mutate(`Measure` = gsub("#", "number of", `Measure`)) %>%
  distinct()

cat(paste0("Story Behind the Curve updated on ", format(df$`Modify Date`[1], format = "%b %d, %Y"), "\n\n"))

measures = unique(df$Measure)

for (m in measures) {
  cat(paste0("**", m, "** \n\n"))
  cat(paste0(df$`Note Text`[df$Measure==m], "\n\n"))
}

```