```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

data <- sc_questions %>%
  filter(`Service ID` == id)

budget <- summary %>%
  filter(`Service ID` == id) %>%
  ungroup() %>%
  select(-`Agency Name`, -`Agency Name - Cleaned`, -`Service ID`, -`Service Name`, -`FY24 Dollars - PROP`, -`FY24 Positions - PROP`)

colnames(budget) <- c("Fund", "Actual $", "Actual Pos", "Adopted $", "Adopted Pos", "CLS $", "CLS Pos")

```
*The Bureau of the Budget and Management Research Budget Proposals*

## Service: `r service`

**Agency Name**: `r agency`

**Pillar**: `r pillar`

**Service Description**: `r description`

### Budget Information

*Budget data is from BPFS as of* `r Sys.Date() `.

```{r budget_summary, echo = FALSE, results = 'asis', warning=FALSE, out.width="100%"}
##replace budget data source

budget %>% 
  adorn_totals(fill = 0) %>%
  format_table_numbers() %>%
  knitr::kable(format = "latex", escape = TRUE, booktabs = TRUE, align = c("l", rep("r", 6))) %>%
  kable_styling(latex_options = c("striped","HOLD_position")) %>%
  add_header_above(c("Funds" = 1, "FY22" = 2, "FY23" = 2, "FY24" = 2), bold = TRUE) %>%
  row_spec(dim(budget)[1]+1, bold = TRUE) %>%
  row_spec(0, bold = TRUE)

```

### Budget Proposal

**FY24 Proposed Budget**: `r scales::dollar(fy24_dollars)`

**FY24 Proposed Positions**: `r fy24_positions `


```{r budget_proposal, echo = FALSE, results = 'asis', warning=FALSE, out.width="100%"}

df <- data %>%
  select(`Budget Proposal`) %>%
  separate(`Budget Proposal`, into = c("Budget", "Question 1", "Question 2", "Question 3"), sep = "\\s+[1-3].\\s")

cat(paste(df$`Question 1`, "\n\n"))

cat(paste(df$`Question 2`, "\n\n"))

cat(paste(df$`Question 3`, "\n\n"))

# cat(ifelse(nchar(df$`Question 1`) <= 94, paste(df$`Question 1`, "\n\n", "No answer provided", "\n\n"), paste(df$`Question 1`, "\n\n")))
# 
# cat(ifelse(nchar(df$`Question 2`) <= 96, paste(df$`Question 2`, "\n\n", "No answer provided", "\n\n"), paste(df$`Question 2`, "\n\n")))
# 
# cat(ifelse(nchar(df$`Question 3`) <= 51, paste(df$`Question 2`, "\n\n", "No answer provided", "\n\n"), paste(df$`Question 3`, "\n\n")))

```

### Service Questions and Responses

#### Mayor's Action Plan
```{r MAP, echo = FALSE, results = 'asis', warning = FALSE}

df <- data %>%
  select(`Mayor's  Action Plan`) %>%
  separate(`Mayor's  Action Plan`, into = c("Question 4", "Question 5", "Question 6"), sep = "\\s+[4-6].\\s") %>%
  mutate(`Question 4` = str_replace(`Question 4`, "4. ", ""))

cat(paste(df$`Question 4`, "\n\n"))

cat(paste(df$`Question 5`, "\n\n"))

cat(paste(df$`Question 6`, "\n\n"))
```


#### Equity
```{r equity, echo = FALSE, results = 'asis', warning = FALSE}

df <- data %>%
  select(Equity) %>%
    separate(Equity, into = c("Equity Description", "Question 7", "Question 8"), sep = "\\s+[7-8].\\s") %>%
  mutate(`Question 7` = str_replace(`Question 7`, "7. ", ""),
         `Question 8` = str_replace(`Question 8`, "8. ", ""),
         `Equity Description` = str_replace(`Equity Description`, "Service Delivery & Equity", ""))

cat(paste0("*", df$`Equity Description`, "*", " \n\n"))

cat(paste(df$`Question 7`, "\n\n"))

cat(paste(df$`Question 8`, "\n\n"))

```


#### Resiliency
```{r resiliency, echo = FALSE, results = 'asis', warning = FALSE}
df <- data %>%
  select(`Resiliency`) %>%
  separate(Resiliency, into = c("Resiliency Description", "Question 9"), sep = "               ") %>%
  mutate(`Question 9` = str_replace(`Question 9`, "9. ", ""),
         `Resiliency Description` = str_replace(`Resiliency Description`, "Service Delivery & Resiliency", ""))

cat(paste0("*", df$`Resiliency Description`, "*", " \n\n"))

cat(df$`Question 9`)

```


### Performance Data
```{r pm_table, echo = FALSE, warning = FALSE, out.width = "100%"}
  
output <- sc_pms %>% filter(`Service ID` == id) %>%
  select(Measure:`Target 2024`)

colnames(output) <- c("Measure", "Actual", "Target", "Actual", "Target", "Actual", "Target", "Target")

output %>%
  knitr::kable(format = "latex", escape = TRUE, booktabs = TRUE, align = c("l", rep("r", 7))) %>%
  kable_styling(latex_options = c("striped","HOLD_position")) %>%
  add_header_above(c("Measure" = 1, "2021" = 2, "2022" = 2, "2023" = 2, "2024" = 1), bold = TRUE) %>%
  column_spec(1, width = "2in") %>%
  row_spec(0, bold = TRUE)

```
